Solution

Package used
```{r}
options(java.parameters = c("-XX:+UseConcMarkSweepGC", "-Xmx8192m"))
require(xlsx)
require(sqldf)
require(ggplot2)
require(mclust)
require(rpart)
require(rpart.plot)
```

data input
```{r}
sale_data <- read.xlsx("Sale_Data.xlsx","Sales_Record")
product_information <- read.xlsx("Sale_Data.xlsx","Product_Information")
sale_data
product_information
```

Data Observation / Cleansing
```{r}
#prove there are 70680 sales records
count <- nrow(sale_data)
paste("There are",count,"sales records.")
checking_record <- sqldf("select 
                  DISTINCT sale_data.订单号 
                  from sale_data 
                  ")
checking_record
#prove product name in both dataset are synchronized
checking_product_name <- sqldf("select 
                  sale_data.订单号, sale_data.商品, product_information.商品 
                  from sale_data 
                  inner join product_information 
                  on sale_data.商品 = product_information.商品
                  where sale_data.商品 != product_information.商品
                  ")
checking_product_name
#prove product_price = actual paid
checking_price <- sqldf("select 
                  sale_data.订单号, sale_data.商品, sale_data.应付金额, sale_data.实际金额
                  from sale_data 
                  where 应付金额 != 实际金额
                  ")
checking_price
#list any uncleaned data for cleansing if necessary
sale_data$支付时间 <- as.POSIXct(sale_data$支付时间, tz = "UTC", format = "%m/%d/%Y %H:%M:%S")
names(product_information)[names(product_information) == '商品'] <- '商品1'
sale_data
product_information
```

Merge Data
```{r}
combine <- sqldf("select * from sale_data inner join product_information on (sale_data.商品 = product_information.商品1)")
combine
```

Mission 1.1 According to the merged dataset, suppose each location only have one vendor machine. Extract the Sales record from the merged dataset and store the data separately based on the Vendor machine location "A", "B", "C", "D", "E".
```{r}
sales_by_location <- sqldf("select * from combine
                           order by 地点")
sales_by_location
```

Mission 1.2 Calculate each vending machine’s sales revenue and number of orders for April 2017, and also compute the overall total sales revenue and total number of orders across all vending machines. Display the results in a table within the report.
```{r}
combine2 <- combine
combine2$支付时间 <- as.character(combine2$支付时间)
combine2
count_order_apr <- sqldf("select 地点 as Location, count(地点) as Sale_Volume,sum(实际金额) as Revenue from combine2 where 支付时间 like '2017-04-%' group by 地点")
count_order_apr
```

Mission 1.3 Summaries the monthly average Revenue of each Vendor machine and also it is daily average Sale volume.
```{r}
combine3 <- combine
combine3$支付时间 <- as.Date(combine3$支付时间)
combine3
avg_order_per_month <- sqldf("select 地点 as Location, strftime('%m', 支付时间) as Month,avg(实际金额) as Revenue from combine3 where Month is not null group by 地点,Month")
order_per_day <- sqldf("select 地点 as Location, strftime('%d', 支付时间) as Day,count(*) as Revenue from combine3 where Day is not null group by 地点,Day ")
avg_order_per_month
order_per_day
```

Mission2.1 visualise the top 5 sale product in June 2017 using bar chart
```{r}
count_product <- combine2
count_product <- sqldf("select 商品, count(商品) as amont from count_product where 支付时间 like '2017-06-%' group by 商品 order by amont desc")
count_product
top5 <- count_product[1:5,]
top5
ggplot(top5, aes(x = 商品, y = amont, fill = 商品)) +
  geom_bar(stat = "identity") +
  labs(title = "Best Five Sale Products")
```

Mission 2.2 visualise all vendor machine revenue trend in monthly basis and also its growth rate in bar chart.
```{r}
total_order_per_month <- sqldf("select 地点 as Location, strftime('%m', 支付时间) as Month,sum(实际金额) as Revenue from combine3 where Month is not null group by 地点,Month")
total_order_per_month
ggplot(total_order_per_month, aes(x = Month, y = Revenue,group = Location, color = Location)) +
  geom_line() +
  theme(legend.position = "right")+
  labs(title = "Vendor Machine Revenue Trend In Monthly Basis",y = "Monthly Revenue",x = "Month")
loc_A <- total_order_per_month[total_order_per_month$Location=="A",]
loc_B <- total_order_per_month[total_order_per_month$Location=="B",]
loc_C <- total_order_per_month[total_order_per_month$Location=="C",]
loc_D <- total_order_per_month[total_order_per_month$Location=="D",]
loc_E <- total_order_per_month[total_order_per_month$Location=="E",]
loc_A$Diff <- c(0, diff(loc_A$Revenue))
loc_B$Diff <- c(0, diff(loc_B$Revenue))
loc_C$Diff <- c(0, diff(loc_C$Revenue))
loc_D$Diff <- c(0, diff(loc_D$Revenue))
loc_E$Diff <- c(0, diff(loc_E$Revenue))
loc_A
loc_B
loc_C
loc_D
loc_E
ggplot(loc_A, aes(x = Month, y = Diff)) +
  geom_bar(stat = "identity",
           show.legend = FALSE) +
  labs(title = "Growth Rate of Vendor Machine A",y = "Monthly Revenue",x = "Month")
ggplot(loc_B, aes(x = Month, y = Diff)) +
  geom_bar(stat = "identity",
           show.legend = FALSE) +
  labs(title = "Growth Rate of Vendor Machine B",y = "Monthly Revenue",x = "Month")
ggplot(loc_C, aes(x = Month, y = Diff)) +
  geom_bar(stat = "identity",
           show.legend = FALSE) +
  labs(title = "Growth Rate of Vendor Machine C",y = "Monthly Revenue",x = "Month")
ggplot(loc_D, aes(x = Month, y = Diff)) +
  geom_bar(stat = "identity",
           show.legend = FALSE) +
  labs(title = "Growth Rate of Vendor Machine D",y = "Monthly Revenue",x = "Month")
ggplot(loc_E, aes(x = Month, y = Diff)) +
  geom_bar(stat = "identity",
           show.legend = FALSE) +
  labs(title = "Growth Rate of Vendor Machine E",y = "Monthly Revenue",x = "Month")
```

Mission2.3 plot margin revenue proportion for each vendor machine. Suppose the margin revenue rate of beverage and non-beverage is 25% and 20% respectively.
```{r}
product_loc <- sqldf("select 地点 as Location,商品 as Product,大类 as Category,实际金额 as Price from combine order by 地点")
product_loc

loc_A <- product_loc[product_loc$Location=="A",]
loc_B <- product_loc[product_loc$Location=="B",]
loc_C <- product_loc[product_loc$Location=="C",]
loc_D <- product_loc[product_loc$Location=="D",]
loc_E <- product_loc[product_loc$Location=="E",]

loc_A_D <- loc_A[loc_A$Category=="饮料",]
loc_B_D <- loc_B[loc_B$Category=="饮料",]
loc_C_D <- loc_C[loc_C$Category=="饮料",]
loc_D_D <- loc_D[loc_D$Category=="饮料",]
loc_E_D <- loc_E[loc_E$Category=="饮料",]

loc_A_ND <- loc_A[loc_A$Category=="非饮料",]
loc_B_ND <- loc_B[loc_B$Category=="非饮料",]
loc_C_ND <- loc_C[loc_C$Category=="非饮料",]
loc_D_ND <- loc_D[loc_D$Category=="非饮料",]
loc_E_ND <- loc_E[loc_E$Category=="非饮料",]

loc_A_D$Revenue_Rate <- loc_A_D$Price*0.25
loc_B_D$Revenue_Rate <- loc_B_D$Price*0.25
loc_C_D$Revenue_Rate <- loc_C_D$Price*0.25
loc_D_D$Revenue_Rate <- loc_D_D$Price*0.25
loc_E_D$Revenue_Rate <- loc_E_D$Price*0.25

loc_A_ND$Revenue_Rate <- loc_A_ND$Price*0.2
loc_B_ND$Revenue_Rate <- loc_B_ND$Price*0.2
loc_C_ND$Revenue_Rate <- loc_C_ND$Price*0.2
loc_D_ND$Revenue_Rate <- loc_D_ND$Price*0.2
loc_E_ND$Revenue_Rate <- loc_E_ND$Price*0.2

loc_A_D
loc_B_D
loc_C_D
loc_D_D
loc_E_D

loc_A_ND
loc_B_ND
loc_C_ND
loc_D_ND
loc_E_ND

loc_A_cal <- data.frame(rbind(sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_A_D"),sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_A_ND")))
loc_B_cal <- data.frame(rbind(sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_B_D"),sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_B_ND")))
loc_C_cal <- data.frame(rbind(sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_C_D"),sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_C_ND")))
loc_D_cal <- data.frame(rbind(sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_D_D"),sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_D_ND")))
loc_E_cal <- data.frame(rbind(sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_E_D"),sqldf("select Location, Category, sum(Revenue_Rate) as Total_Revenue_Rate from loc_E_ND")))

loc_A_cal
loc_B_cal
loc_C_cal
loc_D_cal
loc_E_cal

pie(
   loc_A_cal$Total_Revenue_Rate,
   labels=loc_A_cal$Category,
   )
pie(
   loc_B_cal$Total_Revenue_Rate,
   labels=loc_B_cal$Category,
   )
pie(
   loc_C_cal$Total_Revenue_Rate,
   labels=loc_C_cal$Category,
   )
pie(
   loc_D_cal$Total_Revenue_Rate,
   labels=loc_D_cal$Category,
   )
pie(
   loc_E_cal$Total_Revenue_Rate,
   labels=loc_E_cal$Category,
   )
```

Mission 2.4 - plot the total revenue of each machines in April 2027 by bubble chart
```{r}

```

Mission 2.5 - plot the revenue of Vendor machine C in June, July, and August and summmarise the data by heatmap graph.
```{r}

```
Mission 3.1
Use any machine learning approach to auto labelling the salse status of each brevage products in each Vendor machine. There are three types of labels : unsaleable, normal, trending. In which, unsaleable means the salse status was uncertain, and normal means there is no observable sale pattern, treding mean the sale is good. 

```{r}

```

Mission 3.2  Use any machine learning approach to classify the sale segnments of different types of product category by the relationship of the Category total Revenue.
```{r}

```
