Solution

Package used
```{r}
options(java.parameters = c("-XX:+UseConcMarkSweepGC", "-Xmx8192m"))
require(xlsx)
require(sqldf)
require(ggplot2)
require(mclust)
require(rpart)
require(rpart.plot)
```

data input
```{r}
sale_data <- read.xlsx("Sale_Data.xlsx","Sales_Record")
product_information <- read.xlsx("Sale_Data.xlsx","Product_Information")
sale_data
product_information
```

Data Observation / Cleansing
```{r}
#prove there are 70680 sales records
count <- nrow(sale_data)
paste("There are",count,"sales records.")
checking_record <- sqldf("select 
                  DISTINCT sale_data.订单号 
                  from sale_data 
                  ")
checking_record
#prove product name in both dataset are synchronized
checking_product_name <- sqldf("select 
                  sale_data.订单号, sale_data.商品, product_information.商品 
                  from sale_data 
                  inner join product_information 
                  on sale_data.商品 = product_information.商品
                  where sale_data.商品 != product_information.商品
                  ")
checking_product_name
#prove product_price = actual paid
checking_price <- sqldf("select 
                  sale_data.订单号, sale_data.商品, sale_data.应付金额, sale_data.实际金额
                  from sale_data 
                  where 应付金额 != 实际金额
                  ")
checking_price
#list any uncleaned data for cleansing if necessary
sale_data$支付时间 <- as.POSIXct(sale_data$支付时间, tz = "UTC", format = "%m/%d/%Y %H:%M:%S")
names(product_information)[names(product_information) == '商品'] <- '商品1'
sale_data
product_information
for (col in colnames(sale_data)) {
  for (row in seq_len(nrow(sale_data))) {
    if (is.na(sale_data[row, col])) {
      paste("Column:", col, "- Row:", row, "is missing\n")
    }
  }
}

```

Merge Data
```{r}

```

Mission 1.1 According to the merged dataset, suppose each location only have one vendor machine. Extract the Sales record from the merged dataset and store the data separately based on the Vendor machine location "A", "B", "C", "D", "E".
```{r}

```

Mission 1.2 Calculate each vending machine’s sales revenue and number of orders for April 2017, and also compute the overall total sales revenue and total number of orders across all vending machines. Display the results in a table within the report.
```{r}

```

Mission 1.3 Summaries the monthly average Revenue of each Vendor machine and also it is daily average Sale volume.
```{r}

```

Mission2.1 visualise the top 5 sale product in June 2017 using bar chart
```{r}

```

Mission 2.2 visualise all vendor machine revenue trend in monthly basis and also its growth rate in bar chart.
```{r}

```

Mission2.3 plot margin revenue proportion for each vendor machine. Suppose the margin revenue rate of beverage and non-beverage is 25% and 20% respectively.
```{r}

```

Mission 2.4 - plot the total revenue of each machines in April 2027 by bubble chart
```{r}

```

Mission 2.5 - plot the revenue of Vendor machine C in June, July, and August and summmarise the data by heatmap graph.
```{r}

```
Mission 3.1
Use any machine learning approach to auto labelling the salse status of each brevage products in each Vendor machine. There are three types of labels : unsaleable, normal, trending. In which, unsaleable means the salse status was uncertain, and normal means there is no observable sale pattern, treding mean the sale is good. 

```{r}

```

Mission 3.2  Use any machine learning approach to classify the sale segnments of different types of product category by the relationship of the Category total Revenue.
```{r}

```
